Likelihood-Based Inference for Generalized Linear Mixed Models: Inference with Package \pkg{glmm}

### 2016-09-08 JSS/article.tex
added a line to the paper

%% almost as usual
\author{Achim Zeileis\\Universit\"at Innsbruck \And 
        Second Author\\Plus Affiliation}
\title{ Likelihood-Based Inference for Generalized Linear Mixed Models: Inference with Package \pkg{glmm}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Achim Zeileis, Second Author} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Package foo} %% without formatting
\Shorttitle{\pkg{foo}: A Capitalized Title} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  The abstract of the article.
}
\Keywords{keywords, comma-separated, not capitalized, \proglang{Java}}
\Plainkeywords{keywords, comma-separated, not capitalized, Java} %% without formatting
%% at least one keyword must be supplied

>>>>

%% almost as usual
\author{Christina Knudson\\Macalester College \And 
        Charles Geyer\\University of Minnesota \And 
        Galin Jones\\University of Minnesota}
\title{ Likelihood-Based Inference for Generalized Linear Mixed Models: Inference with Package \pkg{glmm}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Christina Knudson, Charles Geyer, Galin Jones} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Package foo} %% without formatting
\Shorttitle{\pkg{glmm}: Likelihood-Based Inference for Generalized Linear Mixed Models} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  The abstract of the article.
}
\Keywords{generalized linear mixed models, maximum likelihood, likelihood-based inference, mixed models, Monte Carlo likelihood approximation, Monte Carlo maximum likelihood}
\Plainkeywords{generalized linear mixed models, maximum likelihood, likelihood-based inference, mixed models, Monte Carlo likelihood approximation, Monte Carlo maximum likelihood} %% without formatting
%% at least one keyword must be supplied
